Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-23 extended_catalog/paper/extended_catalog.tex
added alexs comments

\begin{abstract}
We present a new method for quantifying the spatial extension of sources
with the Large Area Telescope (LAT), the primary science instrument on
the {\em \fermi Gamma-ray Space Telescope} (\fermi).  Spatial extension
is an important characteristic for correctly associating LAT sources with
their counterparts at other wavelengths. We perform a series of Monte
Carlo simulations to validate this tool and calculate the LAT's threshold
for detecting the spatial extension of sources.  We then use this tool
to test all sources in the two-year source catalog for extension. We
report the detection of nine spatially extended sources in addition to
the twelve spatially extended sources reported in the second \fermi-LAT
Catalog (2FGL).
\end{abstract}

@@

Each of the previously detected extended LAT sources was spatially
resolved by a dedicated analysis of the particular source so
we expect that a systematic scan of all LAT detected sources
could uncover additional spatially extended sources.  For these
reasons, in Section~\ref{analysis_methods_section} we present
a new method for analyzing spatially extended LAT sources. In
Section~\ref{monte_carlo_validation} we demonstrate that this tool
can be used for an unbiased statistical test of the extension of
LAT sources and in Section~\ref{extension_sensitivity} we calculate
the LAT's detection threshold to resolve the extension of a source.
In Section~\ref{extended_source_search_method} we describe a search for
new spatially extended LAT sources and in Section~\ref{validate_known}
we reanalyzing the twelve previously detected extended sources
included in 2FGL.  In Section~\ref{test_2lac_sources} we further
validate our extension test by testing the extension of Active
galactic nucleus (AGN) believed to be unresolvable. Finally, in
Section~\ref{new_ext_srcs_section} we present the detection of the
extension of nine spatially extended sources that were reported in 2FGL
but not previously spatially resolved.

@@

To validate our method, we test LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the cores
of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
to be spatially resolvable by the LAT and provide a good calibration source to
demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
halos around AGNs have been hypothesized \citep{pair_halo_paper} which
could be resolved by the LAT However, no such halo has been discovered
in the LAT data so far.

Following 1FGL, the LAT Collaboration published a list 
of sources that
had a high probability association with AGN 
called 1LAC \citep{first_agn_cat}.
1FGL had 709 1FGL sources associated with 671 distinct AGN at high
latitude ($|b|>10\deg$).  
Using two years of data and 2FGL, the LAT Collaboration
associated 1016 2FGL sources
with AGN called 2LAC \citep{second_agn_cat}.
To avoid systematic problems with AGN classification, we
selected 885 out of the 1016 AGN which made it into the clean AGN sub-sample.  An AGN
association is considered clean only if it has a high probability
of association $P\ge 80\%$, if it is the only AGN associated with the
catalog source, and if there are no flags on the source in 2FGL. These
last two conditions are important for our analysis. Source
confusion may look like a spatially extended source and flagged catalog
sources may correlate with unmodeled structure in the diffuse emission.

Of the 885 clean AGN, we select 783 of these 2FGL sources which
are significantly-detected above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is
shown in Figure~\ref{agn_ts_ext}. Overlaid on the plot is the
$\chi^2/2$ distribution of Equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good agreement with the
theoretical distribution.  Two sources had $\tsext>10$.  One was due
to incorrectly automatically removing a nearby catalog sources (see
Section~\ref{extended_source_search_method}) and the other was due to a
failure of convergence of the point hypothesis.  This result demonstrates
that we can use \tsext as a measure of the statistical significance of
the detection of the extension of a source.

We should clarify that the LAT PSF used in this study was determined
empirically by fitting the observed shape of bright AGN (see
Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
test are not extended is not surprising.  This validation analysis is
not suitable to reject any hypotheses about the existence of mpc-scale
halos around AGN.

@@

Nine extended sources not included in 2FGL were found using this search.
Three were found in our search using 1-100 \gev photons and six were
found in our search using 10-100 \gev photons.  The fit properties of
these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
This table includes for each source the best fit position, extension,
spectrum, source significance, and significance of extension.

@@

The source 2FGL\,J0823.0$-$4246 was found 
using 1-100 \gev photons to have an 
extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
with an extension
significance of $\tsext=46.3$.  The source was fit to a position of
$(l,b)=(260\fdg32,-3\fdg28)$.  
This source is coincident with the one-year
catalog source 1FGL\,J0823.3$-$4248.
\hl{
Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source
and Figure~\ref{snr_seds} shows the LAT spectrum of it.
}

To get a good fit of the source, we had to remove from our background
model the nearby catalog
sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
extended source.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
we conclude that this is an extended source.  These modifications are
shown in Figure~\ref{1FGL_J0823.3-4248}.

\hl{1
This extended source is spatially coincident with the middle-aged
SNR Puppis A.  Puppis A has been studied in detail in radio
(\cite{puppis_a_vla}, and references therein) and  X-ray 
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
Mosaic \rosat observations of Puppis A produced the highest
resolution X-ray image of the source
and contours corresponding to this
image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
inferred \gev size \citep{rosat_puppis_a}.
Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
which leads to a 1-100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.

@@

The source 2FGL\,J1627.0$-$2425c was found using 1-100 \gev photons to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$.  The best fit position is
$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
is seen in Figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=20.0$
is smaller than \tsext, we conclude that this is an extended source.

\hl{
This source is in a region of remarkably complicated diffuse emission.
Even though it is $16\deg$ from the Galactic plane, the source is on
top of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in the infrared.  The region also has
abundant molecular and atomic gas traced by CO and HI but also plenty of
dark gas, the kind that we find only by its association with dust emission
\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Infared and 
${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c}. There is good
spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
so this source might represent an inadequacy in the diffuse
$\gamma$-ray model.
}

@@

The source 2FGL\,J1712.4$-$3941 was found using 1-100 \gev
photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
with an extension significance of $\tsext=39.6$.  This source was
fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

@@

The source 2FGL\,J0851.7$-$4635 was found 
using 10-100 \gev photons to have an
extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
with an extension
significance of $\tsext=87.2$.  The source was fit to a position of
$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

@@

To get a good fit of the source, we had to remove from
our background model the nearby catalog
sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL\,J0854.7$-$4501 to
$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
in the presence of of the extended source.  In addition, we removed from
our model the
further away catalog sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
because they were not significant above 10 \gev.  After modifying
the region, we found that \tsinc=16.1 which is less than \tsext so we
conclude that the source is extended.

@@

The source 2FGL\,J1615.0$-$5051 was found using 10-100 \tev
photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
with an extension significance of \tsext=16.3.  The source
was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
This source is coincident with the one-year catalog source
1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of this source.

This source is less than $1\deg$ away from 2FGL\,J1615.2$-$5138 which is
also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
To get a good fit of both sources, we had to model both sources as
being spatially extended and iteratively fit the position and extension
of each source until obtaining a global best fit.  Before doing this,
We removed from our background model the source 2FGL\,J1614.9$-$5212 because it is
part of 2FGL\,J1615.2$-$5138's. Furthermore, we removed from our model the nearby catalog
sources 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
significant above 10 \gev.  These modifications are further described
in the caption to Figure~\ref{1FGL_J1613.6-5100c}.  After modifying
the region, we found that \tsinc=11.9 which is less than \tsext so we
conclude that the source is extended.

2FGL\,J1615.2$-$5138 is spatially coincident with the extended
\tev source HESS\,J1616$-$508 \citep{hess_plane_survey}.  In
Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616$-$508 are overlaid
on 2FGL\,J1615.0$-$5051.  The H.E.S.S. experiment measured an
extension $0.136\pm 0.008$ when fitting the source with an elliptical
2D Gaussian surface brightness.  This size corresponds to a 68\% containment
radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0$-$5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616$-$508.

@@

The source 2FGL\,J1615.2$-$5138 was found using 10-100 \gev
photons to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
with an extension significance of \tsext=48.0.  The source was fit to a
position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
with the one-year catalog source 1FGL\,J1614.7$-$5138c.  Because 2FGL
J1615.2$-$5138 is close to 2FGL\,J1615.0$-$5051, the same model described
in Section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
sources. Both sources can be seen in Figure~\ref{1FGL_J1613.6-5100c}.
For 2FGL\,J1615.2$-$5138, \tsinc=37.0 which is less than \tsext so we
conclude that the source is extended.

This source is spatially coincident with the extended
\tev source HESS\,J1614$-$518 \citep{hess_plane_survey}. In
Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614$-$518 are overlaid
on 2FGL\,J1615.2$-$5138.  The H.E.S.S. experiment measured a 2D Gaussian
extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0.15\pm0.02$
in the semi-major and semi-minor axis. This size corresponds
to a 68\% containment size of $\rsixeight=0\fdg35\pm0\fdg03$
and $0.23\pm0.03$.  This elliptical size matches the LAT size
$\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
that the LAT spectrum of 2FGL\,J1615.2$-$5138 connects smoothly to
the H.E.S.S spectrum of HESS\,J1614$-$518.  Further data collected by
H.E.S.S. in 2007 helped to resolve a double peaked structure in the
H.E.S.S. data but no spectral variation across the source, suggesting
that the emission is not the confusion of physically separate sources
\citep{closer_look_hess_j1614-518}.  The source was also detected by
CANGAROO-III \citep{cangaroo_j1614-518}.

\hl{
There are five nearby pulsars, but none are luminous enough to
provide the required energy output required to power the $\tev$ 
emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
is spatially coincident with a young open cluster Pismis 22
\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.
\suzaku detected two
promising X-ray candidates. Source A is an extended source consistent
with the peak of HESS\,J1614$-$518 and source B coincident with Pismis 22
and towards the center but in a relatively dim region of HESS\,J1614$-$518
\citep{suazku_hess_j1614_518}.  Three hypothesis have been presented to
explain this emission; either source A is an SNR powering the $\gamma$-ray
emission, source A is a PWN powered by an undiscovered pulsar in either
source A or B, and finally that the emission may arise from hadronic 
acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
}

@@

The source 2FGL\,J1632.4$-$4753c was found 
using 10-100 \gev photons to
have an extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ 
with an extension
significance of \tsext=64.5.  The source was fit to a position of
$(l,b)=(336\fdg41,0\fdg22)$.  This source is coincident with the one
year catalog source 1FGL\,J1632.9$-$4802c.  Figure~\ref{1FGL_J1632.9-4802c}
shows a counts map of this source.

To get a good fit of the source, we had to remove from our background model
three catalog sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
2FGL J1634.4$-$4743c.4-4820c that were part of the extended source..
We then iteratively relocalized the source 2FGL\,J1635.4$-$4717c
to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
$(l,b)=(336\fdg97,-0\fdg07)$ while fitting the extension of
2FGL\,J1632.4$-$4753c.  In addition we removed from our model four
farther away two-year catalog sources 2FGL\,J1638.0$-$4703c, 
2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
were not significant above 10 \gev.  These modifications are shown
in Figure~\ref{1FGL_J1632.9-4802c}.  To test for source confusion,
we compared the likelihood fitting this region as one extended source
to the likelihood fitting this region as two point sources. We found
$\tsinc=40.6$ which is less than \tsext so we conclude
that this is an extended source.

This extended source is spatially coincident with the extended
\tev source HESS\,J1632$-$478 \citep{hess_plane_survey}.
In Figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632$-$478
are overlaid on 2FGL\,J1635.4$-$4717c.  H.E.S.S measured a 
extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
semi-major and semi-minor axes when fitting the source with an
elliptical 2D Gaussian surface brightness.  This corresponds to a 68\%
containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
along the semi-major and semi-minor axis. This size is consistent with
the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
shows that the LAT spectrum of 2FGL\,J1635.4$-$4717c connects smoothly to
the H.E.S.S spectrum of HESS\,J1632$-$478.

\hl{
\cite{hess_plane_survey} argued that HESS\,J1632$-$478
is positionally coincident with the hard X-ray source
IGR\,J1632-4751 observed by INTEGRAL, \xmmnewton, and \asca
\citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
but this source is suspected to be an galactic X-Ray Binary so the $\gamma$-ray
extension disfavors the association.  Further observations by
\xmmnewton reveal extended emission of size $\sim32\arcsec\times15\arcsec$
and inside point-like emission coincident with the peak
H.E.S.S. emission \citep{hess_j1632_478_xmm_newton}.  They found
in archival MGPS-2 data a spatially coincident extended radio source
\citep{most_survey_galactic_plane}.  The positional match argues for a
single synchrotron processes producing X-ray and \gev and \tev radiation,
likely due to a PWNe.  The increased \gev and \tev size compared
to the X-ray size has previously been observed in several aging PWNe
including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
a different synchrotron cooling time for the electrons producing X-rays
and \tev gamma rays.
}

@@

2FGL reported on the detection of twelve sources
previously known as extended. Using
two years of LAT data and a new analysis method, we present on 
the detection of nine additional extended sources. We also reanalyze
the spatial shape of the extended sources in 2FGL.  Finding a coherent
source extension with different frequencies, especially at \tev energies,
allows us to firmly associate the LAT source in many cases.

>>>>

\begin{abstract}
We present a new method for quantifying the spatial extension of sources
with the Large Area Telescope (LAT), the primary science instrument on
the {\em \fermi Gamma-ray Space Telescope} (\fermi).  Spatial extension
is an important characteristic for correctly associating LAT sources with
their counterparts at other wavelengths. We perform a series of Monte
Carlo simulations to validate this tool and calculate the LAT's threshold
for detecting the spatial extension of sources.  We then 
test all sources in the two-year source catalog for extension. We
report the detection of nine spatially extended sources in addition to
the twelve spatially extended sources reported in the second \fermi-LAT
Catalog (2FGL).
\end{abstract}

@@

Each of the previously detected extended LAT sources was spatially
resolved by a dedicated analysis of the particular source so
we expect that a systematic scan of all LAT detected sources
could uncover additional spatially extended sources.  For these
reasons, in Section~\ref{analysis_methods_section} we present
a new method for analyzing spatially extended LAT sources. In
Section~\ref{monte_carlo_validation} we demonstrate that this tool
can be used for an unbiased statistical test of the extension of
LAT sources and in Section~\ref{extension_sensitivity} we calculate
the LAT's detection threshold to resolve the extension of a source.
In Section~\ref{extended_source_search_method} we describe a search for
new spatially extended LAT sources and in Section~\ref{validate_known}
we reanalyzing the twelve previously detected extended sources
included in 2FGL.  In Section~\ref{test_2lac_sources} we further
demonstrate that our detection method does not misidentify
point sources as being extended 
by testing the extension of Active
galactic nucleus (AGN) believed to be unresolvable. Finally, in
Section~\ref{new_ext_srcs_section} we present the detection of the
extension of nine spatially extended sources that were reported in 2FGL
but not previously spatially resolved.

@@

To validate our method, we test LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the
cores of kiloparsec-scale jets of distant galaxies.  Therefore AGN are
not expected to be spatially resolvable by the LAT and provide a good
calibration source to demonstrate that our extension detection method
does not misidentify point sources as being extended.  We note that
megaparsec-scale $\gamma$-ray halos around AGNs have been hypothesized
\citep{pair_halo_paper} to be resolvable by the LAT. However, no such
halo has been discovered in the LAT data so far.

Following 1FGL, the LAT Collaboration published the First LAT AGN Catalog
(1LAC), a list of sources that had a high probability association with
AGN \citep{first_agn_cat}.  1FGL had 709 1FGL sources associated with 671
distinct AGN at high latitude ($|b|>10\deg$).  Using two years of data
and 2FGL, the Second LAT AGN Catalog (2LAC) associated 1016 2FGL sources
with AGN \citep{second_agn_cat}.  To avoid systematic problems with AGN
classification, we selected 885 out of the 1016 AGN which made it into
the clean AGN sub-sample.  An AGN association is considered clean only
if it has a high probability of association $P\ge 80\%$, if it is the
only AGN associated with the catalog source, and if there are no flags
on the source in 2FGL. These last two conditions are important for our
analysis. Source confusion may look like a spatially extended source
and flagged catalog sources may correlate with unmodeled structure in
the diffuse emission.

Of the 885 clean AGN, we select 783 of these 2FGL sources which
are significantly-detected above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is
shown in Figure~\ref{agn_ts_ext}. Overlaid on the plot is the
$\chi^2/2$ distribution of Equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good agreement with the
theoretical distribution.  Two sources had $\tsext>10$.  One was due
to the incorrect removal of a nearby catalog sources from
the sky model (see
Section~\ref{extended_source_search_method}) and the other was due to a
failure of convergence of the point hypothesis.  This result demonstrates
that we can use \tsext as a measure of the statistical significance of
the detection of the extension of a source.

We should clarify that the LAT PSF used in this study was determined
empirically by fitting the observed shape of bright AGN (see
Section~\ref{systematic_errors_on_extension}). Finding that the AGN we
test are not extended is not surprising.  This validation analysis is
not suitable to reject any hypotheses about the existence of megaparsec-scale
halos around AGN.

@@

Nine extended sources not included in 2FGL were found using this search.
Three were found in our search using 1 \gev 100 \gev photons and six were
found in our search using 10 \gev to 100 \gev photons.  The fit properties of
these nine sources is summarized in Table~\ref{new_ext_srcs_table}.
This table includes for each source the best fit position, extension,
spectrum, source significance, and significance of extension.

@@

The source 2FGL\,J0823.0$-$4246 was found 
to have an 
extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
with an extension
significance of $\tsext=46.3$
using 1 \gev to 100 \gev photons.  This source was fit to a position of
$(l,b)=(260\fdg32,-3\fdg28)$.  
This source is coincident with the one-year
catalog source 1FGL\,J0823.3$-$4248.
\hl{
Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source
and Figure~\ref{snr_seds} shows the LAT spectrum of it.
}
To get a good fit of this source, we removed from our background
model the nearby catalog
sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
extended source.  These modifications are
shown in Figure~\ref{1FGL_J0823.3-4248}.

\hl{
This extended source is spatially coincident with the middle-aged
SNR Puppis A.  Puppis A has been studied in detail in radio
(\cite{puppis_a_vla}, and references therein) and  X-ray 
(\cite{rosat_puppis_a,suzaku_puppis_a}, and references therein)
Mosaic \rosat observations of Puppis A produced the highest
resolution X-ray image of this source
and contours corresponding to this
image are overlaid on Figure~\ref{1FGL_J0823.3-4248} and match the
inferred \gev size \citep{rosat_puppis_a}.
Puppis A's distance was estimated at 2.2 kpc \citep{reynoso_1995,reynoso_2003}
which leads to a 1 \gev to 100 \gev luminosity of $\sim 3\times 10^{34}$ ergs/\s.

@@

The source 2FGL\,J1627.0$-$2425c was found  to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$
using 1 \gev to 100 \gev photons.  The best fit position is
$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
is seen in Figure \ref{1FGL_J1628.6-2419c}.

\hl{
This source is in a region of remarkably complicated diffuse emission.
Even though it is $16\deg$ from the Galactic plane, this source is on
top of the core of the Ophiuchus molecular cloud which contains massive
star-forming regions that are bright in the infrared.  The region also has
abundant molecular and atomic gas traced by CO and HI but also plenty of
dark gas found only by its association with dust emission
\citep{isabelle_dark_gass}. Embedded star-forming regions make it even
more challenging to measure the column density of dust.  Infared and 
${}^{12}\text{CO}$ ($J=1\rightarrow 0$)
contours are overlaid on Figure~\ref{1FGL_J1628.6-2419c}. There is good
spatial correlation with the \gev emission \citep{iras_rho_ophiuci,co_rho_ophiuci}
so this source might represent an inadequacy in the diffuse
$\gamma$-ray model.
}

@@

The source 2FGL\,J1712.4$-$3941 was found 
photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
with an extension significance of $\tsext=39.6$
using 1 \gev to 100 \gev.  This source was
fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  this source
is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

@@

The source 2FGL\,J0851.7$-$4635 was found 
to have an
extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
with an extension
significance of $\tsext=87.2$
using 10 \gev to 100 \gev photons.  This source was fit to a position of
$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

@@

To get a good fit of this source, removed from
our background model the nearby catalog
sources 2FGL\,J0853.5$-$4711, 2FGL\,J0848.5$-$4535, and 2FGL\,J0855.4$-$4625
which are part of the extended source.  In addition, we relocalized
the position of the nearby catalog source 2FGL\,J0854.7$-$4501 to
$(l,b)=(266\fdg24,0\fdg49)$ to better fit its position at high energies
in the presence of of the extended source.  In addition, we removed from
our model the
further away catalog sources 2FGL\,J0858.0$-$4815 and 2FGL\,J0901.7$-$4655
because they were not significant above 10 \gev.

@@

The source 2FGL\,J1615.0$-$5051 was found 
photons to have an extension of $0\fdg33\pm0\fdg04_\stat\pm0\fdg01_\sys$
with an extension significance of \tsext=16.3
using 10 \gev to 100 \gev.  This source
was fit to a position of $(l,b)=(332\fdg38,-0\fdg14)$.
This source is coincident with the one-year catalog source
1FGL\,J1613.6$-$5100c. Figure~\ref{1FGL_J1613.6-5100c} shows a counts map
of this source.

This source is less than $1\deg$ away from 2FGL\,J1615.2$-$5138 which is
also spatially extended (see Section~\ref{section_2FGL_J1615.2-5138}).
To get a good fit of both sources, we modeled both sources as
being spatially extended and iteratively fit the position and extension
of each source until obtaining a global best fit.  Before doing this,
We removed from our background model the source 2FGL\,J1614.9$-$5212 because it is
part of 2FGL\,J1615.2$-$5138's. Furthermore, we removed from our model the nearby catalog
sources 2FGL\,J1619.7$-$5040c and 2FGL\,J1620.6$-$5111c because they were not
significant above 10 \gev.  These modifications are further described
in the caption to Figure~\ref{1FGL_J1613.6-5100c}.

2FGL\,J1615.2$-$5138 is spatially coincident with the extended
\tev source HESS\,J1616$-$508 \citep{hess_plane_survey}.  In
Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1616$-$508 are overlaid
on 2FGL\,J1615.0$-$5051.  The H.E.S.S. experiment measured an
extension $0.136\pm 0.008$ when fitting this source with an elliptical
2D Gaussian surface brightness.  This size corresponds to a 68\% containment
radius of $\rsixeight=0\fdg21\pm0\fdg01$. This size is comparable to the LAT
size $\rsixeight=0\fdg27\pm0\fdg03$ (see Section~\ref{compare_source_size}).
Figure~\ref{hess_seds} shows that the LAT spectrum of 2FGL\,J1615.0$-$5051
connects smoothly to the H.E.S.S spectrum of HESS\,J1616$-$508.

@@

The source 2FGL\,J1615.2$-$5138 was found 
photons to have an extension of $0\fdg42\pm0\fdg03_\stat\pm0.01_\sys$
with an extension significance of \tsext=48.0
using 10 \gev to 100 \gev.  This source was fit to a
position of $(l,b)=(331\fdg66,-0\fdg66)$.  This source is coincident
with the one-year catalog source 1FGL\,J1614.7$-$5138c.  Because 2FGL
J1615.2$-$5138 is close to 2FGL\,J1615.0$-$5051, the same model described
in Section~\ref{section_2FGL_J1615.0-5051} was used to analyze both
sources. Both sources can be seen in Figure~\ref{1FGL_J1613.6-5100c}.

This source is spatially coincident with the extended
\tev source HESS\,J1614$-$518 \citep{hess_plane_survey}. In
Figure~\ref{1FGL_J1613.6-5100c}, contours of HESS\,J1614$-$518 are overlaid
on 2FGL\,J1615.2$-$5138.  The H.E.S.S. experiment measured a 2D Gaussian
extension of $\sigma=0\fdg23\pm0\fdg02$ and $\sigma=0.15\pm0.02$
in the semi-major and semi-minor axis. This size corresponds
to a 68\% containment size of $\rsixeight=0\fdg35\pm0\fdg03$
and $0.23\pm0.03$.  This elliptical size matches the LAT size
$\rsixeight=0\fdg35\pm0\fdg03$.  Figure~\ref{hess_seds} shows
that the LAT spectrum of 2FGL\,J1615.2$-$5138 connects smoothly to
the H.E.S.S spectrum of HESS\,J1614$-$518.  Further data collected by
H.E.S.S. in 2007 helped to resolve a double peaked structure in the
H.E.S.S. data but no spectral variation across this source, suggesting
that the emission is not the confusion of physically separate sources
\citep{closer_look_hess_j1614-518}.  The source was also detected by
CANGAROO-III \citep{cangaroo_j1614-518}.

\hl{
There are five nearby pulsars, but none are luminous enough to
provide the energy output required to power the $\tev$ 
emission \citep{closer_look_hess_j1614-518}.  HESS\,J1614$-$518
is spatially coincident with a young open cluster Pismis 22
\citep{hess_1614_landi_atel,closer_look_hess_j1614-518}.
\suzaku detected two
promising X-ray candidates. Source A is an extended source consistent
with the peak of HESS\,J1614$-$518 and source B coincident with Pismis 22
and towards the center but in a relatively dim region of HESS\,J1614$-$518
\citep{suazku_hess_j1614_518}.  Three hypothesis have been presented to
explain this emission; either source A is an SNR powering the $\gamma$-ray
emission, source A is a PWN powered by an undiscovered pulsar in either
source A or B, and finally that the emission may arise from hadronic 
acceleration in the stellar winds of Pisim 22 \citep{cangaroo_j1614-518}.
}

@@

The source 2FGL\,J1632.4$-$4753c was found 
to
have an extension of $0\fdg44\pm0\fdg04_\stat\pm0\fdg03_\sys$ 
with an extension
significance of \tsext=64.5
using 10 \gev to 100 \gev photons.  This source was fit to a position of
$(l,b)=(336\fdg41,0\fdg22)$.  This source is coincident with the one
year catalog source 1FGL\,J1632.9$-$4802c.  Figure~\ref{1FGL_J1632.9-4802c}
shows a counts map of this source.

To get a good fit of this source, we removed from our background model
three catalog sources 2FGL\,J1631.7$-$4720c, 2FGL\,J1630.2$-$4752,
2FGL J1634.4$-$4743c.4-4820c that were part of the extended source..
We then iteratively relocalized the source 2FGL\,J1635.4$-$4717c
to $(l,b)=(337\fdg23,0\fdg35)$ and 2FGL\,J1636.3$-$4740c to
$(l,b)=(336\fdg97,-0\fdg07)$ while fitting the extension of
2FGL\,J1632.4$-$4753c.  In addition we removed from our model four
farther away two-year catalog sources 2FGL\,J1638.0$-$4703c, 
2FGL\,J1628.1$-$4857c, 2FGL\,J1630.1$-$4615, 2FGL\,J1639.8$-$4921c because they
were not significant above 10 \gev.  These modifications are shown
in Figure~\ref{1FGL_J1632.9-4802c}.

This extended source is spatially coincident with the extended
\tev source HESS\,J1632$-$478 \citep{hess_plane_survey}.
In Figure~\ref{1FGL_J1632.9-4802c}, contours of  HESS\,J1632$-$478
are overlaid on 2FGL\,J1635.4$-$4717c.  H.E.S.S measured a 
extension of $\sigma=0.21\pm0.05$ and $0.06\pm0.04$ along the
semi-major and semi-minor axes when fitting this source with an
elliptical 2D Gaussian surface brightness.  This corresponds to a 68\%
containment size $\rsixeight=0\fdg31\pm0\fdg08$ and $0\fdg09\pm0\fdg06$
along the semi-major and semi-minor axis. This size is consistent with
the LAT size $\rsixeight=0\fdg36\pm0\fdg04$.  Figure~\ref{hess_seds}
shows that the LAT spectrum of 2FGL\,J1635.4$-$4717c connects smoothly to
the H.E.S.S spectrum of HESS\,J1632$-$478.

\hl{
\cite{hess_plane_survey} argued that HESS\,J1632$-$478
is positionally coincident with the hard X-ray source
IGR\,J1632-4751 observed by INTEGRAL, \xmmnewton, and \asca
\citep{Igr_J16320-4751_circ,xmm_newton_IGR_J16320-4751,asca_plane_survey},
but this source is suspected to be an galactic X-Ray Binary so the $\gamma$-ray
extension disfavors the association.  Further observations by
\xmmnewton reveal extended emission of size $\sim32\arcsec\times15\arcsec$
and inside point-like emission coincident with the peak
H.E.S.S. emission \citep{hess_j1632_478_xmm_newton}.  They found
in archival MGPS-2 data a spatially coincident extended radio source
\citep{most_survey_galactic_plane}.  The positional match argues for a
single synchrotron processes producing X-ray and \gev and \tev radiation,
likely due to a PWNe.  The increased \gev and \tev size compared
to the X-ray size has previously been observed in several aging PWNe
including HESS\,J1825$-$137 \citep{hess_j1825_xmm_newton,hess_j1825_hess},
HESS\,J1640$-$465 \citep{hess_plane_survey,xmm_newton_hess_j_1640-466},
and Vela X \citep{vela_x_rosat,vela_x_hess}.  This can be explained by
a different synchrotron cooling time for the electrons producing X-rays
and \tev $\gamma$-rays.
}

@@

2FGL reported the detection of twelve sources
previously resolved by the LAT at \gev energies. Using
two years of LAT data and a new analysis method, we present on 
the detection of nine additional extended sources. We also reanalyze
the spatial shape of the extended sources in 2FGL.  Finding a coherent
source extension with different frequencies, especially at \tev energies,
allows us to firmly associate the LAT source in many cases.
